On the presentation of orthogonal groups over polynomial rings

### 2019-05-24 dl-paper.tex
Strengthened statement of Corollary 2

\begin{corollary} \label{Kgen-strong} For $A$ and $M$ as in~\cref{thmStein} and arbitrary fixed root $\gamma\in \Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by
 $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\pm \gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$. \end{corollary}
\begin{proof} Choose some ordering on $\Phi$ with respect to which $\gamma$ becomes the maximal positive root. 
 Invoking~\eqref{C4} of~\cref{Crels} with $\xi = 1$, $s = m$, $t = X\eta$ we obtain that modulo 
 $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to 
 $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. 
 Arguing by induction on the height of $\alpha$ we conclude that $c_\alpha(m, X\eta)$ for all $\alpha \in \Phi^+$
 belong to the subgroup generated by $\overline{\St}(\Phi, A[X], XA[X])$ and $c_\gamma(m, X\eta)$.
 Similar argument also works for the negative roots, and the required assertion now follows. \end{proof}

@@

\begin{rem}\label{rem:c-DS} It is easy to check that $P_\alpha(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\St(\Phi, A, M) \hookrightarrow \St(\Phi, A[X, X\inv])$.
In particular, it contains the relative Dennis--Stein and Steinberg symbols.
It is also clear that $P_\alpha(0)$ contains the elements $c_{\pm \beta}(f, X\xi)$ for all $\beta \in Z(\alpha)$
 (they can be factored as products of two elements of type 2 or 3). \end{rem}

@@

The second assertion can be verified in a straightforward manner. \end{proof}

\subsection{The subgroups \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties}
Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df} Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
 \begin{enumerate}
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}

>>>>

\begin{corollary} \label{Kgen-strong} For $A$ and $M$ as in~\cref{thmStein} and arbitrary fixed root $\gamma$ of an irreducible simply-laced root system $\Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$. \end{corollary}
\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into relation~\eqref{C4} of~\cref{Crels} we obtain that modulo 
 $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. The assertion of the corollary now easily follows from the irreducibility of $\Phi$.
\end{proof}

@@

\begin{rem}\label{rem:c-DS} It is easy to check that $P_\alpha(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\St(\Phi, A, M) \hookrightarrow \St(\Phi, A[X, X\inv])$.
In particular, it contains the relative Dennis--Stein and Steinberg symbols.
It is also clear that $P_\alpha(0)$ contains the elements $c_{\beta}(f, X\xi)$ for all $\beta \in Z(\alpha)$
 (they can be factored as products of two elements of type 2 or 3). \end{rem}

@@

The second assertion can be verified directly using~\eqref{eq:symbol-properties}. \end{proof}

\subsection{The subgroups \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties}
Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df} Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
 \begin{enumerate}
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}
